Decomposing labelled proof theory for intuitionistic modal logic

### 2019-08-06 caleidoscope/caleidoscope.tex
adding more information

%%% General
\input{aiml_macros}
%\newcommand{\F}{\mathcal{F}}
%\newcommand{\M}{\mathcal{M}}
%\newcommand{\G}{\mathcal{G}}
\newcommand{\B}{\mathcal{B}}
%\newcommand{\Left}{\mathcal{L}}
%\newcommand{\Right}{\mathcal{R}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marianela{If it is a long paper, we can give us the space to explain the system with details. So we can add something like the next section (presenting the system by parts and then put the whole system).}

@@

As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}. In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics. This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation. In the next sub-sections, we study each rule of the system $\labIKp$ in detail.

@@

>>>>

%%% General
\input{aiml_macros}
\newcommand{\B}{\mathcal{B}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Equation environments
\newdimen\mydisplayskip
\mydisplayskip=.4\abovedisplayskip
\newenvironment{smallequation}
{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
\newenvironment{smallequation*}
{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
\newenvironment{smallalign}
{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
\newenvironment{smallalign*}
{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
%
\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
%
%
\makeatletter
\newbox\@conclbox
\newdimen\@conclheight
%
%%%%%%
\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
\newcommand\vlderiibase[5]{{%
		\setbox\@conclbox=\hbox{$#3$}\relax%
		\@conclheight=\ht\@conclbox%
		\setbox\@conclbox=\hbox{$%
			\vlderivationnc{%
				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
			}$}%
		\lower\@conclheight\box\@conclbox%
	}}
%%
\newcommand\vlderibase[4]{{%
		\setbox\@conclbox=\hbox{$#3$}\relax%
		\@conclheight=\ht\@conclbox%
		\setbox\@conclbox=\hbox{$%
			\vlderivationnc{%
				\vlin{#1}{#2}{\box\@conclbox}{#4}%
			}$}%
		\lower\@conclheight\box\@conclbox%
	}}
%
\newcommand\vlderidbase[4]{{%
		\setbox\@conclbox=\hbox{$#3$}\relax%
		\@conclheight=\ht\@conclbox%
		\setbox\@conclbox=\hbox{$%
			\vlderivationnc{%
				\vlid{#1}{#2}{\box\@conclbox}{#4}%
			}$}%
		\lower\@conclheight\box\@conclbox%
	}}
	%
	\makeatother
	%
%%%General maths
\newcommand*{\reducesto}{\quad{\leadsto}\quad}

@@

\marianela{If it is a long paper, we can give us the space to explain the system with details. So we can add something like the next section (presenting the system by parts and then put the whole system).}

@@

As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}. In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics. This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation. In the next sub-sections, we study each rule of the new system $\labIKp$ in details (Figure \ref{fig:labIKp}).

@@

\section{A complete and sound system for intuitionistic modal logics}

\begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]

	By induction on number of cuts + (rank,height) of the left-most top-most cut.

	\textbf{Commutative cases:}\label{commutative-cases}

	\begin{smallequation*}
		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
			}{
			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
}
\reducesto
\end{smallequation*}

\begin{smallequation*}\hspace*{-10em}
	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
		}{
		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
	}
}{
\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
}{
\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
}
}
\end{smallequation*}

We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
%
If it does we rewrite it with a fresh variable $v$ first.

%\begin{smallequation*}
%	\reducesto
%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
%%				}{
%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
%%				}
%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
%			}{
%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
%%				}{
%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
%%				}
%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
%			}
%		}
%\end{smallequation*}
%
%\begin{smallalign*}&
%	\text{with } \DD_4 = \quad
%	\vlderivation{
%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
%		}{
%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
%		}
%	}
%	\\&
%	\text{and } \DD_5 = \quad
%	\vlderivation{
%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
%		}{
%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
%		}
%	}
%\end{smallalign*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
}
\end{smallequation*}

\begin{smallequation*}
	\reducesto
	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
	}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
}
\end{smallequation*}

\begin{smallequation*}
	\reducesto
	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
	}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
}
\end{smallequation*}

\begin{smallequation*}
	\reducesto
	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
	}
}
\end{smallequation*}

\begin{smallequation*}\hspace*{-7em}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
}
\reducesto
\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
	}{
	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
}
}
\end{smallequation*}

\begin{smallequation*}\hspace*{-10em}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
}
\reducesto
%	\end{smallequation*}
%	
%	\begin{smallequation*}
\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
	}{
	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
}
}
\end{smallequation*}

\textbf{Key cases:}\label{key-cases}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
			\vlhy{}	
		}
	}{
	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
}
\reducesto
\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
	}{
	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
		\vlhy{}	
	}
}
\reducesto
\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
		}
	}{
	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
	}{
	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
}
}
\reducesto
\end{smallequation*}

\begin{smallequation*}
	\hspace*{-7em}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
			}
			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
		}{
		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
	}
}{
\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
}{
\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
		}
	}{
	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
	}
}
\reducesto
\end{smallequation*}

\begin{smallequation*}\hspace*{-7em}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
		%			}{
		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
		%					\vlhy{}
		%					}
		%				}
		%			}
	}{
	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
		}
	}{
	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
}
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
		}
	}{
	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
	}	
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
		}{
		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
		}
	}
}{
\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
}
\end{smallequation*}
\end{proof}

\begin{lemma}\label{lem:weak}\hbox{}\quad
	\begin{enumerate}
		\item 
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$

		\item 
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$

		\item 
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
	\end{enumerate}
\end{lemma}

\begin{proof}
	Standard
\end{proof}

\begin{lemma}\label{lem:inv}\hbox{}\quad
	\begin{enumerate}
		\item
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.

		\item
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.

		\item 
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.

		\item 
		If there exists a proof 
		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
		then there exists a proof 
		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.

	\end{enumerate}
\end{lemma}
